ggalluvial: Layered Grammar for Alluvial Plots

### 2021-04-03 README.rmd

[![Travis](https://travis-ci.org/corybrunson/ggalluvial.svg?branch=main)](https://travis-ci.org/corybrunson/ggalluvial)
[![CRAN](http://www.r-pkg.org/badges/version/ggalluvial)](https://cran.r-project.org/package=ggalluvial)

>>>>

[![Travis](https://travis-ci.org/corybrunson/ggalluvial.svg?branch=main)](https://travis-ci.org/corybrunson/ggalluvial)
[![CRAN](http://www.r-pkg.org/badges/version/ggalluvial)](https://cran.r-project.org/package=ggalluvial)
[![downloads](https://cranlogs.r-pkg.org/badges/ggalluvial)](https://cran.r-project.org/package=ggalluvial)
